Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2024-12-29 paper/paper.tex
Update paper

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{svg}
\usepackage{comment}
\usepackage{float}

@@

\begin{figure*}[hbt!]
  \centering
  %lresult
  \begin{verbatim}
  \begin{result}
  ... some output ...
  [LR:/tmp/litrepl/python/partial_7b81e1e.txt]
  \end{result}
  \end{verbatim}
  %lnoresult
  \caption{Example output in a verbatim format displayed above two columns.}
  \label{fig:verbatim_example}
\end{figure*}

@@

\begin{figure*}[hbt!]
  \centering
  \begin{verbatim}
  document ::= (code_section | result_section | ignore_section | text)*
  code_section ::= code_bmarker code_section_text code_emarker
  result_section ::= result_bmarker result_section_text result_emarker
  ignore_section ::= ignore_bmarker ignore_section_text ignore_emarker
  \end{verbatim}
  \caption{Example output in a verbatim format displayed above two columns.}
  \label{fig:document_representation}
\end{figure*}

@@

This parsing strategy allows Litrepl to navigate and process documents with
precision, ensuring that relevant sections are evaluated while non-relevant
parts are effectively ignored. By integrating document format-specific markers,
Litrepl maintains flexibility and adaptability in diverse document scenarios.

@@

\section*{References}
\printbibliography

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{svg}
\usepackage{comment}
\usepackage{float}
\usepackage[font=small,skip=0pt]{caption}

@@

\begin{figure*}[hbt!]
  \centering
  \begin{minipage}{\textwidth}
  %lresult
  \begin{verbatim}
  \begin{result}
  ... some output ...
  [LR:/tmp/litrepl/python/partial_7b81e1e.txt]
  \end{result}
  \end{verbatim}
  %lnoresult
  \end{minipage}
  \caption{Example output in a verbatim format displayed above two columns.}
  \label{fig:verbatim_example}
\end{figure*}

@@

\begin{figure*}[hbt!]
  \centering
  \begin{minipage}{\textwidth}
  \begin{verbatim}
  document       ::= (code | result | ignore | text)*
  code           ::= (code-normal | code-comment)
  result         ::= (result-normal | result-comment)
  code-normal    ::= "\begin{MARKER}" text "\end{MARKER}"
  code-comment   ::= "% MARKER" text "% noMARKER"
  result-normal  ::= "\begin{result}" text "\end{result}"
  result-comment ::= "% result" text "% noresult"
  ignore         ::= "% ignore" text "% noignore"
  text           ::= ...
  \end{verbatim}
  \end{minipage}
  \caption{An illustrative grammar template for LaTeX documents where marker
  serves as a parameter configured via command-line arguments for each supported
  interpreter class.}
  \label{fig:document_representation}
\end{figure*}

@@

The template grammars similar to the example are hardcoded for Markdown and
LaTeX document formats. In each run, Litrepl compiles them to the document
parser based on its configuration options using the Lark\cite{Lark} parsing
library.

\section{Discussion}

TODO

@@

\printbibliography
